Manuscript

### 2019-01-02 manuscript_analysis.Rmd
updated stats with AUC_zscore instead of AUC

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

>>>>

# CCLE
ccle_cor_res <- ccle_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ccle_cor_res <- merge(g2p_druggene_tally, ccle_cor_res, by = "Drug_Gene", all.y = TRUE)
ccle_cor_res$n <- ifelse(is.na(ccle_cor_res$n), 0, ccle_cor_res$n)
ccle_cor_res$InG2P <- ifelse(ccle_cor_res$n != 0, "Yes", "No")
ccle_cor_res$Dataset <- "CCLE"
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

# CTRP
ctrp_cor_res <- ctrp_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
ctrp_cor_res <- merge(g2p_druggene_tally, ctrp_cor_res, by = "Drug_Gene", all.y = TRUE)
ctrp_cor_res$n <- ifelse(is.na(ctrp_cor_res$n), 0, ctrp_cor_res$n)
ctrp_cor_res$InG2P <- ifelse(ctrp_cor_res$n != 0, "Yes", "No")
ctrp_cor_res$Dataset <- "CTRP"
ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

# GDSC
gdsc_cor_res <- gdsc_data_g2p_grid %>% group_by(Drug_Gene) %>%
                    summarize(Pearson_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "pearson", use = "complete.obs")$p.value,
                              Pearson_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$estimate,
                              Pearson_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "pearson", use = "complete.obs")$p.value,
                              Spearman_Corr_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_GE = cor.test(y = AUC_zscore, x = RPKM, method = "spearman", use = "complete.obs")$p.value,
                              Spearman_Corr_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$estimate,
                              Spearman_Pval_CN = cor.test(y = AUC_zscore, x = CN, method = "spearman", use = "complete.obs")$p.value)
gdsc_cor_res <- merge(g2p_druggene_tally, gdsc_cor_res, by = "Drug_Gene", all.y = TRUE)
gdsc_cor_res$n <- ifelse(is.na(gdsc_cor_res$n), 0, gdsc_cor_res$n)
gdsc_cor_res$InG2P <- ifelse(gdsc_cor_res$n != 0, "Yes", "No")
gdsc_cor_res$Dataset <- "GDSC"
gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))
